Code publishing tutorial

### 2024-09-07 index.qmd
Fix typo and add RTools and Quarto

- removing legal barriers: adding a appropriate license
- high-level documentation: adding a README file
- archival: uploading to a repository

@@

We will assume you have installed [Git](https://git-scm.com/), [R](https://www.r-project.org/), and [RStudio](https://posit.co/download/rstudio-desktop/).

>>>>

- removing legal barriers: adding an appropriate license
- high-level documentation: adding a README file
- archival: uploading it to a repository

@@

We will assume you have installed [Git](https://git-scm.com/download/), [R](https://cloud.r-project.org/), [RStudio](https://posit.co/download/rstudio-desktop/), and [Quarto](https://quarto.org/docs/download/). Windows users may additionally need [RTools](https://cloud.r-project.org/bin/windows/Rtools/).
